---
title: "General Additive Models"
output: html_notebook
---

This notebook is to explore Generalized Additive Models.
Based on: https://datascienceplus.com/generalized-additive-models/

```{r}
library(gam)
library(ISLR)
attach(Wage)
```

A Generalized Additive Model is a model where the predictions consist of a summation of multiple Non-linear functions

```{r}
model1 <- gam(wage~s(age, df=6) + s(year,df=6) + education ,data=Wage)

summary(model1)
```
# Plotting the model fit

```{r}
par(mfrow=c(1,3))
plot(model1, se=T)
```
# Logistic Regression w GAMs

```{r}

logitgam <- gam(I(wage > 250) ~ s(age, df=4) + s(year,df=4) + education, data=Wage, family=binomial)
plot(logitgam,se=T)

```

lets compare this model with one that is linear in year as well

```{r}

logitgam2 <- gam(I(wage > 250) ~ s(age, df=4) + year + education, data=Wage, family=binomial)
plot(logitgam2, se=T)

```

# Checking Goodness of fit

We will check goodness of fit using anova

```{r}

anova(logitgam, logitgam2, test = "Chisq")

```

